Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-09-09 journal-draft/ettdoc.tex
modify the text about false negative, change figure

Figure~\ref{false_negative} shows the average number of CCCs are decreased slightly.
The reason is that in the process of 
A channel on a CR, which is due to false negative, is very likely ruled out during the interaction in the neighborhood.
Figure~\ref{false_negative_ccc} is shows the size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC with the existence of spectrum sensing false negative.
\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{false_negative.pdf}
  \caption{The number of CCCs per non-singleton cluster with the presence of spectrum sensing false negative}
  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
  \label{false_negative_ccc}
\end{figure}

The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
When false negative exists and increases, the number of singleton clusters increases accordingly.
Actually as to the ROSS variants, the changes of the CDF curves are due to the increasing singleton clusters.
In contrast to the ROSS variants, the clusters resulted from SOC are affected by the sensing errors greatly, \ie when false negative rate is 30\%, a lot more small clusters are generated than that when other false negative rates present.
ROSS variants are resilient to the false negative through the negotiation within the neighborhoods, whereas SOC demonstrates obvious divergence when certain rate of false negative exists.

@@

\subsection{Insights Obtained from the Simulation}
The simulation made with the large CRN network confirms that made with the small CRN network, which is that the average number of CCs along doesn't tell the robustness of the clusters, because the cluster size and the constitution of the cluster also affect the robustness.

The centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against the PUs' activity, besides, it involves the smallest control overhead in the process of clustering.
As distributed schemes, the variants of ROSS outperform SOC considerably on three metrics.
First, the variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
Second, the signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
Third, the sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
Moreover, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
%
As to the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of increased signaling overhead.
%We also notice that as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.

>>>>

Figure~\ref{false_negative_ccc} shows the average number of CCCs decrease slightly when the false negative rate increases.
The size distribution of the ROSS-DGA, ROSS-$\delta$-DGA and SOC is shown in Figure~\ref{false_negative_ccc}.
\begin{figure}[!h]
  \centering
   \includegraphics[width=0.7\linewidth]{false_negative.pdf}
  \caption{The number of CCCs per non-singleton cluster with the presence of spectrum sensing false negative}
  %, there are $x=6$ when $N=100$, $x=12$ when $N=200$, $x=21$ when $N=300$, which is around $2/3$ of the number of average neighbours.
  \label{false_negative_ccc}
\end{figure}
%The influence of the false negative on the sustainability of the clusters can be seen from Figure~\ref{false_negative_CDF}.
For all the schemes, when false negative increases, the number of singleton clusters increases accordingly.
%As to the ROSS variants, the changes of the CDF curves are resulted from the increasing singleton clusters.
The clusters from SOC are affected by the sensing errors greatly, \ie when false negative rate is 30\%, a lot more small clusters are generated than that when other false negative rates present.
SOC demonstrates obvious divergence when certain rate of false negative exists, in contrary, ROSS variants are resilient to the false negative in terms of cluster sizes.
The negotiation within the neighborhoods adopted by ROSS variants rules out the channel which is due to false negative successfully, which doesn't work well in SOC.

@@

\subsection{Insights Obtained from the Simulation}
The simulation with large CRN network confirms the conclusion drawn from the small CRN network.
First, different from the assumption adopted in all the previous works, the average number of CCCs per cluster can tell the robustness against the increasing influence of the primary users.
Second, the centralized clustering scheme is able to form the clusters which satisfy the requirement on cluster size strictly, and the clusters are robust against PUs' increasing activity, besides, it involves the smallest control overhead in the process of clustering.
Third, as distributed schemes, the variants of ROSS outperform SOC considerably in four aspects.
\begin{itemize}
\item The variants of ROSS generate less unclustered nodes than SOC for a given CRN, and the resulted clusters are more robust than SOC when PUs become more active.
\item The signaling overhead involved in ROSS is about half of that needed for SOC, and the signaling messages are much shorter that the latter.
\item The sizes of the clusters generated by ROSS demonstrate smaller discrepancy than that of SOC.
\item The variants of ROSS are more resilient against the imperfect spectrum sensing.
\end{itemize}

Moreover, the ROSS variants with size control features achieve similar performance to the centralized scheme in terms of cluster size, and the cluster robustness is similar when applying the variants of ROSS and the centralized scheme respectively.
%
Among the variants of ROSS, the greedy mechanism in ROSS-DGA helps to improve the performance on cluster size and cluster robustness at the cost of increased signaling overhead.
%We also notice that as a metric, the number of CCs per non-singleton cluster doesn't indicate the robustness of clusters as shown in Figure~\ref{singleton_clusters} and \ref{unclustered_100_200_300}, although it is adopted as the metric in the formation of clusters.
